---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r settings, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-Images/"
)
```

[![Travis-CI Build Status](https://travis-ci.org/jaredlander/HivePlot.svg?branch=master)](https://travis-ci.org/jaredlander/HivePlot)

# Steps to take

1. Turn edgelist into graph
1. Determine number of axes based on number of clusters (or other option)
1. Determine size based on a measure, page rank to start
1. Determine position based on closeness or other measure
1. Plot these coordinates

# Example code

```{r load-packs}
library(igraph)
library(dplyr)
library(magrittr)
library(HivePlot)
```

```{r load-data}
# load data
data(flights)
head(flights)
```

```{r make-graph}
# turn into a graph
g <- graph.data.frame(flights, directed=FALSE)
```

```{r axes}
# Perform clustering to determine number of axes
# it defaults to walktrap.community but any function that returns a clustering should work
g %<>% findAxes
V(g)$axis
```

```{r node-size}
# calculate the size of the nodes, defaulting to page.rank
g %<>% nodeSize
V(g)$nodeSize
```

```{r node-pos}
# find how high up the axis each node should be, defaulting to closeness
g %<>% nodePosition
V(g)$nodePosition
```

# Plotting
Until the package for `[Sigma.js](https://github.com/jaredlander/sigma)` is ready we will use `igraph` for plotting

```{r plot-hive}
plot(g, layout=layout_with_hive(g))
```


# Axis Positions
The first axis will always be the positive side of the x-axis on the cartesian plane (eventually we will be able to specify a starting offset for this first axis)

# More Reading
- http://www.r-bloggers.com/hive-plots-using-r-and-cytoscape/
- http://bib.oxfordjournals.org/content/13/5/627.full
- http://cran.r-project.org/web/packages/HiveR/vignettes/HiveR.pdf
- http://www.vesnam.com/Rblog/viznets3/
- http://www.r-bloggers.com/the-network-structure-of-cran/
